### 2022-11-04 README.Rmd
set chunk options

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "A new method to explicitly estimate the shift of optimum along gradients in multispecies studies"
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "A new method to explicitly estimate the shift of optimum along gradients in multispecies studies"
```
